The Privacy of Private Browsing

### 2013-12-13 finalproject/paper.tex
more applications and conclusion

    \subsection{What Private Browsing Is Not}
    The private browsing modes of Firefox, Chrome, and Internet Explorer are
    designed with the intent of preventing users of the same computer from
    determining what someone was doing on that computer. They do not attempt
    to keep a user's internet activities hidden from that user's internet
    service provider (ISP), and they do not prevent websites from identifying
    that user.\cite{verdi13}\cite{google13}\cite{ie13} Users seeking this kind 
    of anonymity should use the Tor browser, which employs onion routing to 
    connect a user to a destination server. In this type of routing, a random 
    path from the user to the destination is constructed, and content is 
    encrypted at each point in the path. Furthermore, each point (known as a 
    relay or node) only knows from which relay any given piece of network 
    traffic immediately came and the next relay to which it is going. It does 
    not know the original source of the network traffic or its final 
    destination. This is what allows users to keep themselves and their 
    activities anonymous using Tor in a way that the traditional web browsers 
    cannot.\cite{tor13}

    The specifics of the Tor network and how it can be used (and abused) will
    not be considered here. It is mentioned because the Tor browser, like the
    more common web browsers, can leave artifacts of web browsing sessions on
    an individual's computer.

@@

    \subsection{Where To Look}

    Focused analysis of the hard drive itself can reveal the most artifacts.
    One private browsing experiment in which logon information, browser
    history, and cached images were recovered obtained most of the artifacts
    from portions of the hard disk known as \emph{free space} and \emph{slack
    space}. Free space refers to a group of hard drive sectors (called a
    \emph{cluster} that is not allocated to any particular file. Slack space, 
    on the other hand, refers to the space between the end of a file and the 
    end of the cluster in which it is stored. Hard drive clusters are of a 
    fixed size determined by the operating system. Most of the time, when a 
    user saves a file to his or her hard drive, the file is not exactly the
    same size as the cluster in which the operating system puts it.
    Furthermore, when a user ``deletes'' a file from his or her hard drive, the
    file is not really deleted---it is simply marked as available to be
    overwritten if necessary. If a file is eventually stored on the hard drive
    in a cluster that used to be home to a larger (now ``deleted'') file,
    leftover data from the old file will still exist at the end of that
    cluster.

@@

    \subsection{Tor}

@@

  \section{Conclusion}

  \singlespacing
  \begin{thebibliography}{9}
    \bibitem{verdi13}
      Verdi, Michael et al. ``Private Browsing.'' \emph{Mozilla Support}. 
      Mozilla Foundation, 29 Mar. 2013. Web. 10 Dec. 2013. 
      $<$\url{http://support.mozilla.org/en-US/kb/private-browsing-browse-web-
      without-saving-info}$>$.
    \bibitem{google13}
      ``Chrome Browser.'' \emph{Chrome}. Google, 18 Nov. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.google.com/intl/en/chrome/browser/
      features.html#privacy}$>$.
    \bibitem{ie13}
      ``InPrivate Browsing.'' \emph{Microsoft Windows}. Microsoft, 10 Dec. 
      2013. Web. 10 Dec. 2013. $<$\url{http://windows.microsoft.com/en-us/
      internet-explorer/products/ie-9/features/in-private}$>$.
    \bibitem{tor13}
      ``Tor Project: Overview.'' \emph{Tor}. Tor, 7 Dec. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.torproject.org/about/overview.html.en}$>$. 
    \bibitem{ohana13}
      Ohana, Donny, and Narasimha Shashidhar. ``Do Private and Portable Web 
      Browsers Leave Incriminating Evidence? A Forensic Analysis of Residual 
      Artifacts from Private and Portable Web Browsing Sessions.'' IEEE CS 
      Security and Privacy Workshops (SPW), The Westin St. Francis, 
      San Francisco, CA. 23-24 May 2013. Web. 9 Dec. 2013. $<$\url{http://www.
      ieee-security.org/TC/SPW2013/papers/data/5017a135.pdf}$>$

>>>>

    \subsection{What Private Browsing Is Not}
    The private browsing modes of Firefox, Chrome, and Internet Explorer are
    designed with the intent of preventing users of the same computer from
    determining what someone was doing on that computer. They do not attempt
    to keep a user's internet activities hidden from that user's internet
    service provider (ISP), and they do not prevent websites from identifying
    that user.\cite{verdi13}\cite{google13}\cite{ie13}

@@

    \subsection{Where To Look}
    Focused analysis of the hard drive itself can reveal the most artifacts.
    One private browsing experiment in which logon information, browser
    history, and cached images were recovered obtained most of the artifacts
    from portions of the hard disk known as \emph{free space} and \emph{slack
    space}.\cite{ohana13} Free space refers to a group of hard drive sectors 
    (called a \emph{cluster}) that is not allocated to any particular file.
    Slack space,on the other hand, refers to the space between the end of a 
    file and the end of the cluster in which it is stored. Hard drive clusters 
    are of a fixed size determined by the operating system. Most of the time, 
    when a user saves a file to his or her hard drive, the file is not exactly 
    the same size as the cluster in which the operating system puts it.
    Furthermore, when a user ``deletes'' a file from his or her hard drive, the
    file is not really deleted---it is simply marked as available to be
    overwritten if necessary. If a file is eventually stored on the hard drive
    in a cluster that used to be home to a larger (now ``deleted'') file,
    leftover data from the old file will still exist at the end of that
    cluster.

    Artifacts can also be recovered from the computer's memory itself. Cached
    web documents can often be found here.\cite{ohana13} Browsing history,
    logon information, and cookies have been detected after private browsing
    sessions by analyzing a computer's memory. The SQLite databases used by 
    Chrome and Firefox during browsing sessions are generally only stored in 
    memory when private browsing is in use, and their residual data could be 
    detected, as well.\cite{satvat13}

    The Windows pagefile can also reveal private browsing artifacts. This file
    is where the least recently used pages of memory are stored when too many
    applications are competing for the computer's physical memory. Browsing
    history and keywords used in internet search engines have been discovered
    here.\cite{said11}

@@

@@

  \section{Conclusion}
  With all the ways in which private browsing modes can leak information, it
  may seem as though they are completely useless. This is not entirely true.
  While private browsing sessions won't help anyone evade law enforcement, a
  forensic investigation, or the United States government, they are still good
  enough to fool most computer users. Nosy roommates, family members, or
  patrons at the public library are unlikely to go to the lengths discussed in
  this paper to determine what someone else was doing on the internet.

  That said, private browsing modes don't do much to keep a user's identity
  private to the outside world. Users seeking this kind of anonymity should 
  consider using the Tor browser, which employs onion routing to connect them 
  to their destination server. In this type of routing, a random path from the 
  user to the destination is constructed, and content is encrypted at each 
  point in the path. Furthermore, each point (known as a relay or node) only 
  knows from which relay any given piece of network traffic immediately came 
  and the next relay to which it is going. It does not know the original source
  of the network traffic or its final destination. This is what allows users to
  keep themselves and their activities anonymous using Tor in a way that the 
  traditional web browsers cannot.\cite{tor13} Of course, this type of browsing
  can be (ab)used for a whole host of illicit activities, but those are beyond
  the scope of this paper.

  Until Mozilla, Google, and Microsoft reduce the artifacts leaker by their
  respective browsers' private modes, users who are concerned about ``local 
  attackers''---those of the nosy roommate or family member variety who have 
  physical access to their machine---can do their part to keep their private
  information secure. Random access memory, where private browsing artifacts
  have been found, is cleared when a computer is powered down. Shutting down
  the computer after a private browsing session can reduce or eliminate these
  artifacts. Hard drive artifacts, however, are nearly impossible to eradicate.
  The moral of the story is that private browsing is nothing more than a nice
  illusion useful for fooling the computer-illiterate. At the end of the day,
  private browsing really isn't that private at all.

  \singlespacing
  \begin{thebibliography}{9}
    \bibitem{verdi13}
      Verdi, Michael et al. ``Private Browsing.'' \emph{Mozilla Support}. 
      Mozilla Foundation, 29 Mar. 2013. Web. 10 Dec. 2013. 
      $<$\url{http://support.mozilla.org/en-US/kb/private-browsing-browse-web-
      without-saving-info}$>$.
    \bibitem{google13}
      ``Chrome Browser.'' \emph{Chrome}. Google, 18 Nov. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.google.com/intl/en/chrome/browser/
      features.html#privacy}$>$.
    \bibitem{ie13}
      ``InPrivate Browsing.'' \emph{Microsoft Windows}. Microsoft, 10 Dec. 
      2013. Web. 10 Dec. 2013. $<$\url{http://windows.microsoft.com/en-us/
      internet-explorer/products/ie-9/features/in-private}$>$.
    \bibitem{tor13}
      ``Tor Project: Overview.'' \emph{Tor}. Tor, 7 Dec. 2013. Web. 10 Dec. 
      2013. $<$\url{http://www.torproject.org/about/overview.html.en}$>$. 
    \bibitem{ohana13}
      Ohana, Donny, and Narasimha Shashidhar. ``Do Private and Portable Web 
      Browsers Leave Incriminating Evidence? A Forensic Analysis of Residual 
      Artifacts from Private and Portable Web Browsing Sessions.'' IEEE CS 
      Security and Privacy Workshops (SPW), The Westin St. Francis, 
      San Francisco, CA. 23-24 May 2013. Web. 9 Dec. 2013. $<$\url{http://www.
      ieee-security.org/TC/SPW2013/papers/data/5017a135.pdf}$>$
    \bibitem{satvat13}
      Satvat, Kiavash, Matthew Forshaw, Feng Hao, and Ehsan Toreini. ``On The 
      Privacy of Private Browsing - A Forensic Approach.'' Proceedings of the 
      8th International Workshop on Data Privacy Management (DPM '13), Royal 
      Holloway, University of London, Egham, UK. 12-13 Sept. 2013. Web. 9 Dec.
      2013. $<$\url{http://homepages.cs.ncl.ac.uk/feng.hao/files/DPM13.pdf}$>$ 
    \bibitem{said11}
      Said, Huwida, Noora Al Mutawa, Ibtesam Al Awadhi, and Mario Guimaraes.
      ``Forensic Analysis of Private Browsing Artifacts.'' 7th International
      Conference on Innovations in Information Technology, Abu Dhabi, United
      Arab Emirates. 25-27 Apr. 2011. Web. 10 Dec. 2013. $<$\url{http://
      ieeexplore.ieee.org/xpl/articleDetails.jsp?tp=&arnumber=5893816}$>$
